---
title: "assignment2"
output: html_document
date: "2024-08-15"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}

library(baseballr)
library(dplyr)
library(ggplot2)
library(caTools) 
library(knitr) 
library(tibble)
library(RColorBrewer)
library(flux)
library(gridExtra)
library(rockchalk)
library(tidyverse)

```

Question #1 Determine the exponent in the Pythagorean Wins Formula that results in the lowest prediction error for games in recent history (you can decide how many years to include, last 5 years or 10 years, but include all major league games in that time frame). Are we performing better or worse than expected?





```{r pressure, echo=FALSE}


#first, lets figure out the information we need on each league by returning the following

mlb_league(seasons = NULL, sport_id = NULL, league_id = NULL)

#the american league is 103 for league ID, and national league 104, which is what we need for this analysis. We will look at very year since 2018, excluding 2020 due t the season being shortened 

AL2018<-(mlb_standings(season = 2018, league_id = 103))
AL2019<-(mlb_standings(season = 2019, league_id = 103))
AL2021<-(mlb_standings(season = 2021, league_id = 103))
AL2022<-(mlb_standings(season = 2022, league_id = 103))
AL2023<-(mlb_standings(season = 2023, league_id = 103))
NL2018<-(mlb_standings(season = 2018, league_id = 104))
NL2019<-(mlb_standings(season = 2019, league_id = 104))
NL2021<-(mlb_standings(season = 2021, league_id = 104))
NL2022<-(mlb_standings(season = 2022, league_id = 104))
NL2023<-(mlb_standings(season = 2023, league_id = 104))

AllStandings <-rbind(AL2018, AL2019, AL2021, AL2022, AL2023, NL2018, NL2019, NL2021, NL2022, NL2023)

#there a lot of information we don't really need here, so lets clean up the data and remove everything that isnt year, team name, wins, losses, and winning percentage, runs scored, and runs allowed

CleanStandings <- select(AllStandings, 3, 37, 42, 43, 45, 17, 18)

#lets add a column for R, or runs scored/runs allowed

CleanStandings$rsra <- CleanStandings$team_records_runs_scored / CleanStandings$team_records_runs_allowed

```

``` {r} 
# lets do some exponents 

CleanStandings$exp1point2 <- ((CleanStandings$rsra)^1.2)/(((CleanStandings$rsra)^1.2) + 1)
CleanStandings$exp1point3 <- ((CleanStandings$rsra)^1.3)/(((CleanStandings$rsra)^1.3) + 1)
CleanStandings$exp1point4 <- ((CleanStandings$rsra)^1.4)/(((CleanStandings$rsra)^1.4) + 1)
CleanStandings$exp1point5 <- ((CleanStandings$rsra)^1.5)/(((CleanStandings$rsra)^1.5) + 1)
CleanStandings$exp1point6 <- ((CleanStandings$rsra)^1.6)/(((CleanStandings$rsra)^1.6) + 1)
CleanStandings$exp1point7 <- ((CleanStandings$rsra)^1.7)/(((CleanStandings$rsra)^1.7) + 1)
CleanStandings$exp1point8 <- ((CleanStandings$rsra)^1.8)/(((CleanStandings$rsra)^1.8) + 1)
CleanStandings$exp1point9 <- ((CleanStandings$rsra)^1.9)/(((CleanStandings$rsra)^1.9) + 1)
CleanStandings$exp2point0 <- ((CleanStandings$rsra)^2)/(((CleanStandings$rsra)^2) + 1)
CleanStandings$exp2point1 <- ((CleanStandings$rsra)^2.1)/(((CleanStandings$rsra)^2.1) + 1)
CleanStandings$exp2point2 <- ((CleanStandings$rsra)^2.2)/(((CleanStandings$rsra)^2.2) + 1)
CleanStandings$exp2point3 <- ((CleanStandings$rsra)^2.3)/(((CleanStandings$rsra)^2.3) + 1)
CleanStandings$exp2point4 <- ((CleanStandings$rsra)^2.4)/(((CleanStandings$rsra)^2.4) + 1)



``` 

# Then we want to get absolute error, but there is a problem as the winning percentage is characterized as a character and not a number, so we have to fix that 

``` {r} 

CleanStandings$team_records_league_record_pct <- as.numeric(CleanStandings$team_records_league_record_pct) 

CleanStandings$absoluteerror1point2 <- abs((CleanStandings$team_records_league_record_pct) - (CleanStandings$exp1point2))
CleanStandings$absoluteerror1point3 <- abs((CleanStandings$team_records_league_record_pct) - (CleanStandings$exp1point3))
CleanStandings$absoluteerror1point4 <- abs((CleanStandings$team_records_league_record_pct) - (CleanStandings$exp1point4))
CleanStandings$absoluteerror1point5 <- abs((CleanStandings$team_records_league_record_pct) - (CleanStandings$exp1point5))
CleanStandings$absoluteerror1point6 <- abs((CleanStandings$team_records_league_record_pct) - (CleanStandings$exp1point6))
CleanStandings$absoluteerror1point7 <- abs((CleanStandings$team_records_league_record_pct) - (CleanStandings$exp1point7))
CleanStandings$absoluteerror1point8 <- abs((CleanStandings$team_records_league_record_pct) - (CleanStandings$exp1point8))
CleanStandings$absoluteerror1point9 <- abs((CleanStandings$team_records_league_record_pct) - (CleanStandings$exp1point9))
CleanStandings$absoluteerror2point0 <- abs((CleanStandings$team_records_league_record_pct) - (CleanStandings$exp2point0))
CleanStandings$absoluteerror2point1 <- abs((CleanStandings$team_records_league_record_pct) - (CleanStandings$exp2point1))
CleanStandings$absoluteerror2point2 <- abs((CleanStandings$team_records_league_record_pct) - (CleanStandings$exp2point2))
CleanStandings$absoluteerror2point3 <- abs((CleanStandings$team_records_league_record_pct) - (CleanStandings$exp2point3))
CleanStandings$absoluteerror2point4 <- abs((CleanStandings$team_records_league_record_pct) - (CleanStandings$exp2point4))



View(CleanStandings)

```
Now for absolute deviations 

``` {r} 

CleanStandings$deviation1point2 <- abs((CleanStandings$absoluteerror1point2) - (mean(CleanStandings$absoluteerror1point2))) 
CleanStandings$deviation1point3 <- abs((CleanStandings$absoluteerror1point3) - (mean(CleanStandings$absoluteerror1point3)))
CleanStandings$deviation1point4 <- abs((CleanStandings$absoluteerror1point4) - (mean(CleanStandings$absoluteerror1point4)))
CleanStandings$deviation1point5 <- abs((CleanStandings$absoluteerror1point5) - (mean(CleanStandings$absoluteerror1point5)))
CleanStandings$deviation1point6 <- abs((CleanStandings$absoluteerror1point6) - (mean(CleanStandings$absoluteerror1point6)))
CleanStandings$deviation1point7 <- abs((CleanStandings$absoluteerror1point7) - (mean(CleanStandings$absoluteerror1point7)))
CleanStandings$deviation1point8 <- abs((CleanStandings$absoluteerror1point8) - (mean(CleanStandings$absoluteerror1point8)))
CleanStandings$deviation1point9 <- abs((CleanStandings$absoluteerror1point9) - (mean(CleanStandings$absoluteerror1point9)))
CleanStandings$deviation2point0 <- abs((CleanStandings$absoluteerror2point0) - (mean(CleanStandings$absoluteerror2point0)))
CleanStandings$deviation2point1 <- abs((CleanStandings$absoluteerror2point1) - (mean(CleanStandings$absoluteerror2point1))) 
CleanStandings$deviation2point2 <- abs((CleanStandings$absoluteerror2point2) - (mean(CleanStandings$absoluteerror2point2))) 
CleanStandings$deviation2point3 <- abs((CleanStandings$absoluteerror2point3) - (mean(CleanStandings$absoluteerror2point3))) 
CleanStandings$deviation2point4 <- abs((CleanStandings$absoluteerror2point4) - (mean(CleanStandings$absoluteerror2point4))) 

``` 


``` {r}



Mad<- colMeans(CleanStandings[,37:47])
datamad <- data.frame(Mad)
datamad <- rownames_to_column(datamad, var = "deviation")

ggplot(datamad, aes(x = deviation, y = Mad)) + 
  geom_bar(stat = 'identity', position = 'dodge') 



  
  

``` 

## from this we can see the lowest MAD is for the exponent 1.7, so we should use that for our team Pythagorean Wins Formula 

``` {r}


CleanRecords <- select(CleanStandings, 1, 2, 5, 14)

``` 

## We can compare the pythagorean win loss record with th 1.7 exponent to the actual win loss record and see that every year except for 2019 and 2023, the Mariners overperformed expectations 



## Question 2: Pick the three players with the most at-bats this year and determine where they rank at their position compared to the rest of the league. Pick 4 metrics to discuss with at least one coming from seasonal data, one coming from play-by-play data, and one coming from pitch-by-pitch data

``` {r}

batstat <- (fg_batter_leaders(startseason = 2023, endseason = 2023, pos = "np"))

marinersbatters <- batstat %>%
filter(team_name == "SEA")
(marinersbatters[order(marinersbatters$AB, decreasing = TRUE), ]   )

``` 
## From this, we can see that Julio Rodriguez (Center Field), Teoscar Hernandez (Right Field), and Eugenio Suarez are the top three batters in at bats for the Seattle Mariners. 

## We want to compare with four metrics. We Will use wRC+, wOBA, WPA, and Contact percentage

``` {r}

thirdbase <- fg_batter_leaders(startseason = "2023", endseason = "2023", pos = "3b")
thirdbaseclean <- (thirdbase[1:30, c(6, 7, 8, 12, 59,75, 77, 116)]) 
centerfield <- fg_batter_leaders(startseason = "2023", endseason = "2023", pos = "cf")
centerfieldclean <- (centerfield[1:30, c(6, 7, 8, 12, 59,75, 77, 116)]) 
rightfield <- fg_batter_leaders(startseason = "2023", endseason = "2023", pos = "rf") 
rightfieldclean <- (rightfield[1:30, c(6, 7, 8, 12, 59,75, 77, 116)]) 
``` 

Graphs for third base 
``` {r}

ggplot(data = thirdbaseclean, aes(x = PlayerName, y = wOBA)) + 
  geom_point(size = 2) + 
  geom_hline(yintercept = mean(thirdbaseclean$wOBA), color="blue")+
  ggtitle(bquote('Third Baseman wOBA')) +
  theme(plot.title = element_text(hjust = 0.5))+
  scale_color_brewer(palette="YlOrRd") +
  ylab("wOBA") +
  xlab(bquote('Player')) + 
  theme(axis.text.x = element_text(color = "grey20", size = 20, angle = 90, hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 12, angle = 0, hjust = 1, vjust = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 12, angle = 0, hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 12, angle = 90, hjust = .5, vjust = .5, face = "plain")) 


ggplot(data = thirdbaseclean, aes(x = PlayerName, y = wRC_plus)) + 
  geom_point(size = 2) + 
  geom_hline(yintercept = mean(thirdbaseclean$wRC_plus), color="blue")+
  ggtitle(bquote('Third Baseman wRC+')) +
  theme(plot.title = element_text(hjust = 0.5))+
  ylab("wRC+") +
  xlab(bquote('Player')) + 
  theme(axis.text.x = element_text(color = "grey20", size = 20, angle = 90, hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 12, angle = 0, hjust = 1, vjust = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 12, angle = 0, hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 12, angle = 90, hjust = .5, vjust = .5, face = "plain")) 

ggplot(data = thirdbaseclean, aes(x = PlayerName, y = WPA)) + 
  geom_point(size = 2) + 
  geom_hline(yintercept = mean(thirdbaseclean$WPA), color="blue")+
  ggtitle(bquote('Third Baseman WPA+')) +
  theme(plot.title = element_text(hjust = 0.5))+
  ylab("WPA") +
  xlab(bquote('Player')) + 
  theme(axis.text.x = element_text(color = "grey20", size = 20, angle = 90, hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 12, angle = 0, hjust = 1, vjust = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 12, angle = 0, hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 12, angle = 90, hjust = .5, vjust = .5, face = "plain")) 

ggplot(data = thirdbaseclean, aes(x = PlayerName, y = Contact_pct)) + 
  geom_point(size = 2) + 
  geom_hline(yintercept = mean(thirdbaseclean$Contact_pct), color="blue")+
  ggtitle(bquote('Contact Percentage')) +
  theme(plot.title = element_text(hjust = 0.5))+
  ylab("Contact Percentage") +
  xlab(bquote('Player')) + 
  theme(axis.text.x = element_text(color = "grey20", size = 20, angle = 90, hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 12, angle = 0, hjust = 1, vjust = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 12, angle = 0, hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 12, angle = 90, hjust = .5, vjust = .5, face = "plain")) 

``` 

``` {r}
ggplot(data = rightfieldclean, aes(x = PlayerName, y = wOBA)) + 
  geom_point(size = 2) + 
  geom_hline(yintercept = mean(rightfieldclean$wOBA), color="blue")+
  ggtitle(bquote('Right Field wOBA')) +
  theme(plot.title = element_text(hjust = 0.5))+
  scale_color_brewer(palette="YlOrRd") +
  ylab("wOBA") +
  xlab(bquote('Player')) + 
  theme(axis.text.x = element_text(color = "grey20", size = 20, angle = 90, hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 12, angle = 0, hjust = 1, vjust = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 12, angle = 0, hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 12, angle = 90, hjust = .5, vjust = .5, face = "plain")) 


ggplot(data = rightfieldclean, aes(x = PlayerName, y = wRC_plus)) + 
  geom_point(size = 2) + 
  geom_hline(yintercept = mean(rightfieldclean$wRC_plus), color="blue")+
  ggtitle(bquote('Right Field wRC+')) +
  theme(plot.title = element_text(hjust = 0.5))+
  ylab("wRC+") +
  xlab(bquote('Player')) + 
  theme(axis.text.x = element_text(color = "grey20", size = 20, angle = 90, hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 12, angle = 0, hjust = 1, vjust = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 12, angle = 0, hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 12, angle = 90, hjust = .5, vjust = .5, face = "plain")) 

ggplot(data = rightfieldclean, aes(x = PlayerName, y = WPA)) + 
  geom_point(size = 2) + 
  geom_hline(yintercept = mean(rightfieldclean$WPA), color="blue")+
  ggtitle(bquote('Right Field WPA+')) +
  theme(plot.title = element_text(hjust = 0.5))+
  ylab("WPA") +
  xlab(bquote('Player')) + 
  theme(axis.text.x = element_text(color = "grey20", size = 20, angle = 90, hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 12, angle = 0, hjust = 1, vjust = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 12, angle = 0, hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 12, angle = 90, hjust = .5, vjust = .5, face = "plain")) 

ggplot(data = rightfieldclean, aes(x = PlayerName, y = Contact_pct)) + 
  geom_point(size = 2) + 
  geom_hline(yintercept = mean(rightfieldclean$Contact_pct), color="blue")+
  ggtitle(bquote('Right Field Contact Percentage')) +
  theme(plot.title = element_text(hjust = 0.5))+
  ylab("Contact Percentage") +
  xlab(bquote('Player')) + 
  theme(axis.text.x = element_text(color = "grey20", size = 20, angle = 90, hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 12, angle = 0, hjust = 1, vjust = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 12, angle = 0, hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 12, angle = 90, hjust = .5, vjust = .5, face = "plain")) 
``` 

``` {r}

ggplot(data = thirdbaseclean, aes(x = PlayerName, y = wOBA)) + 
  geom_point(size = 2) + 
  geom_hline(yintercept = mean(centerfieldclean$wOBA), color="blue")+
  ggtitle(bquote('Third Baseman wOBA')) +
  theme(plot.title = element_text(hjust = 0.5))+
  scale_color_brewer(palette="YlOrRd") +
  ylab("wOBA") +
  xlab(bquote('Player')) + 
  theme(axis.text.x = element_text(color = "grey20", size = 20, angle = 90, hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 12, angle = 0, hjust = 1, vjust = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 12, angle = 0, hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 12, angle = 90, hjust = .5, vjust = .5, face = "plain")) 


ggplot(data = thirdbaseclean, aes(x = PlayerName, y = wRC_plus)) + 
  geom_point(size = 2) + 
  geom_hline(yintercept = mean(centerfieldclean$wRC_plus), color="blue")+
  ggtitle(bquote('Third Baseman wRC+')) +
  theme(plot.title = element_text(hjust = 0.5))+
  ylab("wRC+") +
  xlab(bquote('Player')) + 
  theme(axis.text.x = element_text(color = "grey20", size = 20, angle = 90, hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 12, angle = 0, hjust = 1, vjust = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 12, angle = 0, hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 12, angle = 90, hjust = .5, vjust = .5, face = "plain")) 

ggplot(data = thirdbaseclean, aes(x = PlayerName, y = WPA)) + 
  geom_point(size = 2) + 
  geom_hline(yintercept = mean(centerfieldclean$WPA), color="blue")+
  ggtitle(bquote('Third Baseman WPA+')) +
  theme(plot.title = element_text(hjust = 0.5))+
  ylab("WPA") +
  xlab(bquote('Player')) + 
  theme(axis.text.x = element_text(color = "grey20", size = 20, angle = 90, hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 12, angle = 0, hjust = 1, vjust = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 12, angle = 0, hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 12, angle = 90, hjust = .5, vjust = .5, face = "plain")) 

ggplot(data = thirdbaseclean, aes(x = PlayerName, y = Contact_pct)) + 
  geom_point(size = 2) + 
  geom_hline(yintercept = mean(centerfieldclean$Contact_pct), color="blue")+
  ggtitle(bquote('Contact Percentage')) +
  theme(plot.title = element_text(hjust = 0.5))+
  ylab("Contact Percentage") +
  xlab(bquote('Player')) + 
  theme(axis.text.x = element_text(color = "grey20", size = 20, angle = 90, hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 12, angle = 0, hjust = 1, vjust = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 12, angle = 0, hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 12, angle = 90, hjust = .5, vjust = .5, face = "plain")) 

``` 

``` {r}
ggplot(data = centerfieldclean, aes(x = PlayerName, y = wOBA)) + 
  geom_point(size = 2) + 
geom_hline(yintercept = mean(centerfieldclean$wOBA), color="blue")+
  ggtitle(bquote('Center Field wOBA')) +
  theme(plot.title = element_text(hjust = 0.5))+
  scale_color_brewer(palette="YlOrRd") +
  ylab("wOBA") +
  xlab(bquote('Player')) + 
  theme(axis.text.x = element_text(color = "grey20", size = 20, angle = 90, hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 12, angle = 0, hjust = 1, vjust = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 12, angle = 0, hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 12, angle = 90, hjust = .5, vjust = .5, face = "plain")) 


ggplot(data = centerfieldclean, aes(x = PlayerName, y = wRC_plus)) + 
  geom_point(size = 2) + 
geom_hline(yintercept = mean(centerfieldclean$wRC_plus), color="blue")+
  ggtitle(bquote('Center Field wRC+')) +
  theme(plot.title = element_text(hjust = 0.5))+
  ylab("wRC+") +
  xlab(bquote('Player')) + 
  theme(axis.text.x = element_text(color = "grey20", size = 20, angle = 90, hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 12, angle = 0, hjust = 1, vjust = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 12, angle = 0, hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 12, angle = 90, hjust = .5, vjust = .5, face = "plain")) 

ggplot(data = centerfieldclean, aes(x = PlayerName, y = WPA)) + 
  geom_point(size = 2) + 
  geom_hline(yintercept = mean(centerfieldclean$WPA), color="blue") +
  ggtitle(bquote('Center Field WPA+')) +
  theme(plot.title = element_text(hjust = 0.5))+
  ylab("WPA") +
  xlab(bquote('Player')) + 
  theme(axis.text.x = element_text(color = "grey20", size = 20, angle = 90, hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 12, angle = 0, hjust = 1, vjust = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 12, angle = 0, hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 12, angle = 90, hjust = .5, vjust = .5, face = "plain")) 

ggplot(data = centerfieldclean, aes(x = PlayerName, y = Contact_pct)) + 
  geom_point(size = 2) + 
  geom_hline(yintercept = mean(centerfieldclean$Contact_pct), color="blue") +
  ggtitle('Center Field Contact Percentage') +
  theme(plot.title = element_text(hjust = 0.5))+
  ylab("Contact Percentage") +
  xlab(bquote('Player')) + 
  theme(axis.text.x = element_text(color = "grey20", size = 20, angle = 90, hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 12, angle = 0, hjust = 1, vjust = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 12, angle = 0, hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 12, angle = 90, hjust = .5, vjust = .5, face = "plain")) 

```

Determine the additional runs we could expect based on seasonal data and possibly through simulation. You can follow the approach outlined in Mathletics (Chapters 3 and 4) or Chapter 9 of Analyzing Baseball Data with R. You may also attempt to come up with a novel approach on your own.

Lets switch Teoscar Hernandez and Isaac Paredes, and start by looking at Hernandez's runs created. 

``` {r}

totalbases <- (rightfield$'1B') + ((rightfield$'2B' * 2 )) + ((rightfield$'3B' * 3 )) + ((rightfield$HR * 4 ))

rightfield$totalbases <- totalbases
  
Hernandezstats <- filter(rightfield, PlayerName == "Teoscar Hernández")


Hernandezouts <- (((0.982)*Hernandezstats$AB) - Hernandezstats$H+ Hernandezstats$GDP + Hernandezstats$SF + Hernandezstats$SB + Hernandezstats$CS) / 26.72

HernandezRunsCreated <- ((Hernandezstats$H + Hernandezstats$BB + Hernandezstats$HBP) * (Hernandezstats$totalbases)) / ((Hernandezstats$AB) + Hernandezstats$BB + Hernandezstats$HBP)

Hernandezrunscreatedpergame <- HernandezRunsCreated/Hernandezouts
``` 

Now for Nolan Jones

``` {r}

Jonesstats <- filter(rightfield, PlayerName == "Nolan Jones")

Jonesouts <- (((0.982)*Jonesstats$AB) - Jonesstats$H+ Jonesstats$GDP + Jonesstats$SF + Jonesstats$SB + Jonesstats$CS) / 26.72

JonesRunsCreated <- ((Jonesstats$H + Jonesstats$BB + Jonesstats$HBP) * (Jonesstats$totalbases)) / ((Jonesstats$AB) + Jonesstats$BB + Jonesstats$HBP)

Jonesrunscreatedpergame <- JonesRunsCreated/Jonesouts

head(Jonesrunscreatedpergame)
head(Hernandezrunscreatedpergame)

``` 
We can see from this that Jones is creating 7.48 runs per game, compared to Hernandez, who was creating 4.72 runs per game 